### 2017-11-22 manuscript.rmd
adjusted table, added latex stylesheet

---
bibliography: manuscript.bib
csl: systematic-biology.csl
output:
  pdf_document:
    fig_caption: yes
---

@@

```{r summary_table, results='asis', echo=FALSE, comment=NA, warning=FALSE}

xtable_summary<-xtable(summary_stats,auto=TRUE)
align( xtable_summary ) <- c('l|',rep('p{0.5in}',ncol(summary_stats)) )
print(xtable_summary, scalebox=0.7, include.rownames=FALSE)

```
Table 1 (at the end of file): Summary statistics for libraries.

@@

####Phylogenetic signal in the character data
```{r phylosig_binaries_declare, echo=F, message=F, warning=F, include=F}
binaries_phylosig = multiPhylosignal(as.matrix(cdata[,c(2,5:8)]), ultratree)
```

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, echo=F, message=F, warning=F}
 # make it xtable
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
align( xtable_PS ) <- c('l|',rep('p{0.5in}',ncol(binaries_phylosig)) )
print(xtable_PS, scalebox=0.7)

### Software versions

>>>>

---
bibliography: manuscript.bib
csl: systematic-biology.csl
output:
  pdf_document:
    fig_caption: yes
    includes:
            in_header: mystyles.sty
---

@@

@@

####Phylogenetic signal in the character data
```{r phylosig_binaries_declare, echo=F, message=F, warning=F, include=F}
binaries_phylosig = multiPhylosignal(as.matrix(cdata[,c(2,5:8)]), ultratree)
names(binaries_phylosig)<-c("K","PICvar obs","PICvar rnd","P-value","Z-score")
```

#####Phylogenetic signal in Binary Traits
```{r phylosig_binaries, results='asis',echo=F, message=F, warning=F}
 # make it xtable
xtable_PS<-xtable(binaries_phylosig,auto=TRUE)
print(xtable_PS, scalebox=0.7,comment=F)

```
```{r summary_table, results='asis', echo=FALSE, comment=NA, warning=FALSE}

xtable_summary<-xtable(summary_stats,auto=TRUE)
align( xtable_summary ) <- c('l|',rep('p{0.5in}',ncol(summary_stats)) )
print(xtable_summary, include.rownames=FALSE,comment=F, floating=FALSE, tabular.environment = "longtable")

```
### Software versions
